Ms 1

### 2017-09-11 ms1/ms1_display.Rmd
updated tables

est2pct = function(x) (exp(x) - 1)*100
mult_est = function(df, m) {
  mutate(df, estimate=m*estimate, std.error=sqrt(m)*std.error)
}
model_ci = function(df) {
  df %>%
    mutate(pct_change=est2pct(estimate),
           ci=1.96*std.error,
           ci_low=est2pct(estimate - ci),
           ci_high=est2pct(estimate + ci),
           change_str=sprintf('%.2f%% (%.2f -- %.2f%%)', pct_change, ci_low, ci_high))
}

@@

Overall, fluoroquinolones changed by a tiny amount, `r fq_change_pct_unadj`% (unadjusted). The adjusted change is `r fq_change_adj` over this period. This included `r fq_names`.

@@

```{r dx_trends}
dx_unadj = read_tsv('tables/dx_trends_table.tsv') %>%
  filter(year %in% c(2011, 2014)) %>%
  left_join(select(totals, year, n_bene), by='year') %>%
  mutate(dxpkp=1000*n_dx/n_bene) %>%
  select(dx_cat, year, dxpkp) %>%
  spread(year, dxpkp) %>%
  mutate(pct_change=(`2014`/`2011`-1)*100) %>%
  arrange(desc(`2011`)) %>%
  mutate_if(is.numeric, function(x) round(x, 2))

@@

dx_to_pde = inner_join(dx_to_pde_unadj,
                       dx_to_pde_adj,
                       by=c('dx_cat', 'antibiotic')) %>%
  # convert model estimates to odds ratios, then to risk ratios,
  # then to adjusted fractional changes, then to percentages
  mutate(or=exp(estimate),
         or_low=exp(ci_low),
         or_high=exp(ci_high),
         rr=risk_ratio_f(or, `2011`),
         rr_low=risk_ratio_f(or_low, `2011`),
         rr_high=risk_ratio_f(or_high, `2011`),
         adj_change=rr-1,
         adj_change_low=rr_low-1,
         adj_change_high=rr_high-1,
         pct_change=(`2014`-`2011`)/`2011`) %>%
  mutate_if(is.numeric, function(x) round(x*100, 2)) %>%
  mutate(adj_change=sprintf('%.2f%% (%.2f -- %.2f%%)', adj_change, adj_change_low, adj_change_high)) %>%
  select(dx_cat, antibiotic, `2011`, `2014`, pct_change, adj_change) %T>%
  kable
```

@@

```{r}
x = dx_trends %>%
  select(-p.value) %>%
  gather('key', 'value', -dx_cat) %>%
  spread(dx_cat, value) %>%
  mutate(antibiotic='dx_trends')

@@

combined_table = bind_rows(x, y, z) %>%
  mutate(antibiotic=factor(antibiotic, levels=c('dx_trends', top_abx)),
         key=factor(key, levels=c('dx_from_pde', '2011', '2014', 'pct_change', 'adj_change'))) %>%
  arrange(antibiotic, key)
```

@@

```{r respiratory}
combined_table %>%
  filter(antibiotic %in% c('dx_trends', 'azithromycin', 'levofloxacin', 'amoxicillin', 'amoxicillin/clavulanate')) %>%
  select(antibiotic, key, not_infectious, asthma, bronchitis, other_resp, pharyngitis, pneumonia, sinusitis, uri) %>%
  kable
```

@@

```{r uti}
combined_table %>%
  filter(antibiotic %in% c('dx_trends', 'ciprofloxacin', 'trimethoprim/sulfamethoxazole', 'nitrofurantoin')) %>%
  select(antibiotic, key, not_infectious, uti, uti_t3) %>%
  kable
```

@@

```{r ssti}
# swo: I removed amox and amox/clav because they mostly
# showed trends in Tier 3, which is confusing
combined_table %>%
  filter(antibiotic %in% c('dx_trends', 'clindamycin', 'cephalexin', 'trimethoprim/sulfamethoxazole')) %>%
  select(antibiotic, key, not_infectious, ssti, ssti_t3) %>%
  kable
```

@@

```{r gi}
combined_table %>%
  filter(antibiotic %in% c('dx_trends', 'ciprofloxacin')) %>%
  select(antibiotic, key, not_infectious, gi, gi_t3) %>%
  kable
```

>>>>

est2pct = function(x) (exp(x) - 1)*100
mult_est = function(df, m) {
  mutate(df, estimate=m*estimate, std.error=sqrt(m)*std.error)
}
model_ci = function(df) {
  df %>%
    mutate(pct_change=est2pct(estimate),
           ci=1.96*std.error,
           ci_low=est2pct(estimate - ci),
           ci_high=est2pct(estimate + ci),
           change_str=sprintf('%.2f (%.2f -- %.2f)', pct_change, ci_low, ci_high))
}

@@

Overall, fluoroquinolones changed by a tiny amount, `r fq_change_pct_unadj`% (unadjusted). The adjusted change is `r fq_change_adj` (%) over this period. This included `r fq_names`.

@@

```{r dx_trends}
dx_unadj = read_tsv('tables/dx_trends_table.tsv') %>%
  #filter(year %in% c(2011, 2014)) %>%
  left_join(select(totals, year, n_bene), by='year') %>%
  mutate(dxpkp=1000*n_dx/n_bene) %>%
  select(dx_cat, year, dxpkp) %>%
  spread(year, dxpkp) %>%
  mutate(pct_change=(`2014`/`2011`-1)*100) %>%
  arrange(desc(`2011`)) %>%
  mutate_if(is.numeric, function(x) round(x, 2))

@@

dx_to_pde = inner_join(dx_to_pde_unadj,
                       dx_to_pde_adj,
                       by=c('dx_cat', 'antibiotic')) %>%
  # convert model estimates to odds ratios, then to risk ratios,
  # then to adjusted fractional changes, then to percentages
  mutate(or=exp(estimate),
         or_low=exp(ci_low),
         or_high=exp(ci_high),
         rr=risk_ratio_f(or, `2011`),
         rr_low=risk_ratio_f(or_low, `2011`),
         rr_high=risk_ratio_f(or_high, `2011`),
         adj_change=rr-1,
         adj_change_low=rr_low-1,
         adj_change_high=rr_high-1,
         pct_change=(`2014`-`2011`)/`2011`) %>%
  mutate_if(is.numeric, function(x) round(x*100, 2)) %>%
  mutate(adj_change=sprintf('%.2f (%.2f -- %.2f)', adj_change, adj_change_low, adj_change_high)) %>%
  select(dx_cat, antibiotic, `2011`, `2014`, pct_change, adj_change) %T>%
  kable
```

@@

```{r}
x = dx_trends %>%
  select(dx_cat, `2011`:`2014`) %>%
  gather('year', 'value', `2011`:`2014`) %>%
  group_by(dx_cat) %>%
  summarize(value=mean(value)) %>%
  # convert to character to fit with other parts
  mutate(value=as.character(value)) %>%
  spread(dx_cat, value) %>%
  mutate(antibiotic='dx', key='mean_per_1kyr')
  # select(-p.value) %>%
  # gather('key', 'value', -dx_cat) %>%
  # spread(dx_cat, value) %>%
  # mutate(antibiotic='dx_trends')

@@

combined_table = bind_rows(x, y, z) %>%
  mutate(antibiotic=factor(antibiotic, levels=c('dx', top_abx)),
         key=factor(key, levels=c('mean_per_1kyr', 'dx_from_pde', '2011', '2014', 'pct_change', 'adj_change'))) %>%
  arrange(antibiotic, key)
```

@@

```{r respiratory}
combined_table %>%
  filter(antibiotic %in% c('dx', 'azithromycin', 'levofloxacin', 'amoxicillin', 'amoxicillin/clavulanate')) %>%
  select(antibiotic, key, asthma, bronchitis, other_resp, pharyngitis, pneumonia, sinusitis, uri) %>%
  kable
```

@@

```{r uti}
combined_table %>%
  filter(antibiotic %in% c('dx', 'ciprofloxacin', 'trimethoprim/sulfamethoxazole', 'nitrofurantoin')) %>%
  select(antibiotic, key, uti, uti_t3) %>%
  kable
```

@@

```{r ssti}
# swo: I removed amox and amox/clav because they mostly
# showed trends in Tier 3, which is confusing
combined_table %>%
  filter(antibiotic %in% c('dx', 'clindamycin', 'cephalexin', 'trimethoprim/sulfamethoxazole')) %>%
  select(antibiotic, key, ssti, ssti_t3) %>%
  kable
```

@@

```{r gi}
combined_table %>%
  filter(antibiotic %in% c('dx', 'ciprofloxacin')) %>%
  select(antibiotic, key, gi, gi_t3) %>%
  kable
```
